---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# kindler

## 中文

用于整理 kindle 杂乱无章的 `My Clippings.txt` 文件，最终按书名输出每本书的笔记。

### 用法

克隆该仓库:

```bash
git clone https://github.com/Shitao5/kindler
```

将 kindle 设备的 `documents` 文件夹复制 `My Clippings.txt` 到这个R项目中，运行 `script.R`：

```{r source1, eval=FALSE}
source("You/path/to/kindler/script.R")
```

### 注意事项

- 使用笔记的位置判定笔记是否重复，该方法不一定精准，可能仍会有重复笔记的情况存在。
- 文件名（`script.R`中的 `title` 变量）中应避免`.`等特殊字符存在。如存在，可以参照第34-45行的方法更改。

### 待办

- [ ] 将其制作为 shiny 应用

## 英文

The goal of **kinder** is to organize kindle's cluttered `My Clippings.txt` file, eventually outputting notes for each book by title.

# Usage

Clone this repo:

```bash
git clone https://github.com/Shitao5/kindler
```

Copy `My Clippings.txt` from the `documents` folder of your kindle device to this R project.

```{r source2, eval=FALSE}
source("You/path/to/kindler/script.R")
```

# note

- Use the location of the note to determine if the note is a duplicate, this method may not be accurate and there may still be duplicate notes.
- The file name (the `title` variable in `script.R`) should avoid `.` and other special characters. If they do exist, you can change them as described in lines 34-45.

# todo

- [ ] Make a shiny app